---
title: "时间序列算法dtw"
author: "haoyi.li"
date: "2018年11月1日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.getlocale()
Sys.setlocale(locale="C") # 解决input string 1 is invalid in this locale的问题
library(dtw)
```

### 1.数据集aami

```{r}
data("aami3a")
str(aami3a)
data("aami3b")
str(aami3b)
plot( main="ECG (mV)", window(cbind(aami3a, aami3b), end=10))
```

### 2.countPaths 
计算满足约束条件的扭曲路径的数目
```{r}
ds<-dtw(1:7+2,1:8,keep=TRUE,step=asymmetric)
countPaths(ds)
plot(ds,type="threeway")
plot(dtw(1:7+2,1:9,keep=TRUE, step=rabinerJuangStepPattern(3,"c")), 
     type="twoway",offset=-3)
```

### 3.dtw
计算动态时间规整，查找两个时间序列之间的最优对齐匹配。

#### 用法
```
dtw(
  x, # 查询时间序列或局部代价矩阵
  y=NULL, # 参考时间序列，当x为代价矩阵时，这个参数无用
  dist.method="Euclidean", # 设置点（局部）使用的距离函数。
  step.pattern=symmetric2, # 一个steppattern对象，描述代价矩阵适用的局部对齐模式
  window.type="none", # 窗口函数，取值: "none", "itakura", "sakoechiba", "slantedband",
  keep.internals=FALSE, # 保存累积成本矩阵、输入和其他内部结构
  distance.only=FALSE, # 是否只计算距离（没有回溯，更快）
  open.end=FALSE, # 2个时间序列结尾端点是否执行开放式对齐
  open.begin=FALSE, # 2个时间序列的开始端点是否执行开放式对齐
  ... # 传递给window.type的附加参数
)
```

#### 返回值说明
```
distance：计算出的最小全局距离，未进行标准化。
normalizedDistance：距离计算，归一化的路径长度，如果规范化是已知的选择步长模式
N,M：查询和参考时间序列的长度
call：创建对象调用的函数
index1： 匹配元素x中的索引
index2：对应y的映射索引
stepPattern：用于计算的Steppattern对象
jmin：open.end=true时，设置引用时间序列匹配的最后一个元素索引
directionMatrix：每个对齐对采取的步骤方向（在所选步骤模式中整数索引的生成规则），当keep.internals=TRUE时，结果才输出
stepsTaken：从对齐开始到结束所采取的步骤列表（所选步骤模式的整数索引）
index1s, index2s：类似index1和index2，不包括多步模式的中间步骤，如asymmetricP05
costMatrix：累积成本矩阵，当keep.internals=TRUE时，结果中才会输出
query, reference：查询及引用时间序列，当keep.internals=TRUE 以及设置x 、y 参数时才会输出
```

#### 代码示例
```{r}
## A noisy sine wave as query
idx<-seq(0,6.28,len=100)
query<-sin(idx)+runif(100)/10
## A cosine is for reference; sin and cos are offset by 25 samples
reference<-cos(idx)
plot(reference)
lines(query,col="blue")
## 查找最佳匹配
alignment<-dtw(query,reference)
## Display the mapping, AKA warping function - may be multiple-valued
## Equivalent to: plot(alignment,type="alignment")
plot(alignment$index1,alignment$index2,main="Warping function")
## Confirm: 25 samples off-diagonal alignment
lines(1:100-25,col="red")

#########
## 通过设置open.end=TRUE,open.begin=TRUE
## 允许部分对齐
##
alignmentOBE <- dtw(query[44:88], reference, keep.internals = TRUE,
                    step.pattern = asymmetric, open.end = TRUE,
                    open.begin = TRUE)
dim(alignmentOBE$costMatrix[1:5,1:5])
plot(alignmentOBE,type="two",off=1)

#########
##
## Subsetting allows warping and unwarping of
## timeseries according to the warping curve.
## See first example below.
##
## Most useful: plot the warped query along with reference
plot(reference)
lines(query[alignment$index1]~alignment$index2,col="blue")
## Plot the (unwarped) query and the inverse-warped reference
plot(query,type="l",col="blue")
points(reference[alignment$index2]~alignment$index1)


#########
##
## Contour plots of the cumulative cost matrix
## similar to: plot(alignment,type="density") or
## dtwPlotDensity(alignment)
## See more plots in ?plot.dtw
##
## keep = TRUE so we can look into the cost matrix
alignment<-dtw(query,reference,keep=TRUE)
contour(alignment$costMatrix,col=terrain.colors(100),x=1:100,y=1:100,
xlab="Query (noisy sine)",ylab="Reference (cosine)")
lines(alignment$index1,alignment$index2,col="red",lwd=2)


#########
##
## An hand-checkable example
##
ldist<-matrix(1,nrow=6,ncol=6) # Matrix of ones
ldist[2,]<-0; ldist[,5]<-0 # Mark a clear path of zeroes
ldist[2,5]<-.01 # Forcely cut the corner
ds<-dtw(ldist) # DTW with user-supplied local cost matrix
da<-dtw(ldist,step=asymmetric) # Also compute the asymmetric
plot(ds$index1,ds$index2,pch=3) # Symmetric: alignment follows the low-distance marked path
points(da$index1,da$index2,col="red") # Asymmetric: visiting 1 is required twice
ds$distance
da$distance
```

### 4.dtwDist
计算一组单变量时间序列之间的相异矩阵

#### 用法
```
dtwDist(mx,my=mx,...)
# dist(mx,my=mx,method="DTW",...)
```

#### 代码示例
```{r}
## Symmetric step pattern => symmetric dissimilarity matrix;
## no problem coercing it to a dist object:
m <- matrix(0,ncol=3,nrow=4)
m <- row(m)
dist(m,method="DTW")
# Old-fashioned call style would be:
# dtwDist(m)
# as.dist(dtwDist(m))


## Find the optimal warping _and_ scale factor at the same time.
## (There may be a better, analytic way)
# Prepare a query and a reference
query<-sin(seq(0,4*pi,len=100))
reference<-cos(seq(0,4*pi,len=100))
# Make a set of several references, scaled from 0 to 3 in .1 increments.
# Put them in a matrix, in rows
scaleSet <- seq(0.1,3,by=.1)
referenceSet<-outer(1/scaleSet,reference)
# The query has to be made into a 1-row matrix.
# Perform all of the alignments at once, and normalize the result.
distanceSet <- dist(t(query),referenceSet,meth="DTW")
# The optimal scale for the reference is 1.0
plot(scaleSet,scaleSet*distanceSet,
     xlab="Reference scale factor (denominator)",
     ylab="DTW distance",type="o",
     main="Sine vs scaled cosine alignment, 0 to 4 pi")


## Asymmetric step pattern: we can either disregard part of the pairs
## (as.dist), or average with the transpose
mm <- matrix(runif(12),ncol=3)
dm <- dist(mm,mm,method="DTW",step=asymmetric); # a crossdist object
# Old-fashioned call style would be:
# dm <- dtwDist(mm,step=asymmetric)
# as.dist(dm)
## Symmetrize by averaging:
(dm+t(dm))/2
## check definition
stopifnot(dm[2,1]==dtw(mm[2,],mm[1,],step=asymmetric)$distance)
```

### 5.dtwPlot
绘制动态时间规整的结果图形

#### 用法
```
## S3 method for class 'dtw'
plot(x, type="alignment", ...)
# an alias for dtw.plot
dtwPlot(x, type="alignment", ...)
dtwPlotAlignment(d, xlab="Query index", ylab="Reference index",plot.type="l", ...)
dtwPlotDensity(d, normalize=FALSE,xlab="Query index", ylab="Reference index",...)
```

#### 参数说明
```
x,d :dtw对象, 通常调用dtw的结果
xlab: x轴标签
ylab: y轴标签
type: 对齐图的一般样式
plot.type: 要绘制的线条类型，基础绘图中调用的线条类型参数。
normalize: 显示每步平均代价而不是累积代价
...: 传递给绘图函数的附加参数
```

#### 代码示例
```{r}
## Same example as in dtw
idx<-seq(0, 6.28, len=100);
query<-sin(idx)+runif(100)/10;
reference<-cos(idx)
alignment<-dtw(query, reference, keep=TRUE);
## A profile of the cumulative distance matrix
## Contour plot of the global cost
dtwPlotDensity(alignment, main="Sine/cosine: symmetric alignment, no constraints")


######
##
## A study of the "Itakura" parallelogram
##
## A widely held misconception is that the "Itakura parallelogram" (as
## described in the original article) is a global constraint. Instead,
## it arises from local slope restrictions. Anyway, an "itakuraWindow",
## is provided in this package. A comparison between the two follows.

## The local constraint: three sides of the parallelogram are seen
ita <- dtw(query, reference, keep=TRUE, step=typeIIIc)
dtwPlot(ita,type="density", main="Slope-limited asymmetric step (Itakura)")

## The local constraint: three sides of the parallelogram are seen
ita <- dtw(query, reference, keep=TRUE, step=typeIIIc)
dtwPlot(ita,type="density", main="Slope-limited asymmetric step (Itakura)")
```

#### 6.dtwPlotThreeWay
绘制查询和参考时间序列及他们之间的对齐样式，并进行图像检验
```{r}
## A noisy sine wave as query
## A cosine is for reference; sin and cos are offset by 25 samples
idx<-seq(0,6.28,len=100);
query<-sin(idx)+runif(100)/10;
reference<-cos(idx)
dtw(query,reference,keep=TRUE)->alignment;
## Beware of the reference's y axis, may be confusing
## Equivalent to plot(alignment,type="three");
dtwPlotThreeWay(alignment);
## Highlight matches of chosen QUERY indices. We will do some index
## arithmetics to recover the corresponding indices along the warping
## curve
hq <- (0:8)/8
hq <- round(hq*100) # indices in query for pi/4 .. 7/4 pi
hw <- (alignment$index1 %in% hq) # where are they on the w. curve?
hi <- (1:length(alignment$index1))[hw]; # get the indices of TRUE elems
dtwPlotThreeWay(alignment,match.indices=hi)
```

### 7.dtwPlotTwoWay
绘制查询和参考时间序列及他们之间的对齐样式，并进行图像检验

#### 用法
```
dtwPlotTwoWay(d,xts=NULL,yts=NULL, offset=0,
ts.type="l",pch=21,
match.indices=NULL,
match.col="gray70", match.lty=3,
xlab="Index", ylab="Query value",
... )
```

#### 代码示例
```{r}
## A noisy sine wave as query
## A cosine is for reference; sin and cos are offset by 25 samples
idx<-seq(0,6.28,len=100);
query<-sin(idx)+runif(100)/10;
reference<-cos(idx)
dtw(query,reference,step=asymmetricP1,keep=TRUE)->alignment;
## Equivalent to plot(alignment,type="two");
dtwPlotTwoWay(alignment)

## Highlight matches of chosen QUERY indices. We will do some index
## arithmetics to recover the corresponding indices along the warping
## curve
hq <- (0:8)/8
hq <- round(hq*100) # indices in query for pi/4 .. 7/4 pi
hw <- (alignment$index1 %in% hq) # where are they on the w. curve?
hi <- (1:length(alignment$index1))[hw]; # get the indices of TRUE elems
## Beware of the reference's y axis, may be confusing
plot(alignment,offset=-2,type="two", lwd=3, match.col="grey50",
match.indices=hi,main="Match lines shown every pi/4 on query");
legend("top",c("Query","Reference"), pch=21, col=1:6)
```

### 8.dtwWindowingFunctions
DTW的全局约束和窗口函数

#### 用法
```
noWindow(iw, jw, ...);
sakoeChibaWindow(iw,jw, window.size,...);
slantedBandWindow(iw,jw,query.size,reference.size, window.size,...);
itakuraWindow(iw,jw,query.size,reference.size, ...);
dtwWindow.plot(fun,query.size=200,reference.size=220,...);
```

#### 参数说明
```
iw： 查询中的索引，自动设置
jw： 引用中的索引，自动设置
query.size： 查询时间序列的大小，自动设置
reference.size： 参考时间序列的大小，自动设置
window.size： 窗口大小，必须设置
fun： 窗口函数
...： 传递给窗口函数的附加参数
```

#### 代码示例
```{r}
## Display some windowing functions
dtwWindow.plot(itakuraWindow, main="So-called Itakura parallelogram window")
dtwWindow.plot(slantedBandWindow, window.size=2, reference=13, query=17, main="The slantedBandWindow at window.size=2")
## Asymmetric step with Sakoe-Chiba band
idx <- seq(0, 6.28, len=100);
query <- sin(idx) + runif(100)/10;
reference <- cos(idx);
asyband <- dtw(query,reference,keep=TRUE, step=asymmetric, window.type=sakoeChibaWindow, window.size=30 );
dtwPlot(asyband, type="density", main="Sine/cosine: asymmetric step, S-C window")
```

### 9.mvm(Minimum Variance Matching algorithm)
最小方差匹配算法，计算时间序列间最小方差匹配对应的步长模式

#### 用法
```
mvmStepPattern(elasticity=20);
```

#### 参数说明
```
elasticity 整型数值: 可跳过最大连续引用元素的数目
```

#### 代码示例
```{r}
## The hand-checkable example given in Fig. 5, ref. [1] above
diffmx <- matrix( byrow=TRUE, nrow=5, c(
0, 1, 8, 2, 2, 4, 8,
1, 0, 7, 1, 1, 3, 7,
-7, -6, 1, -5, -5, -3, 1,
-5, -4, 3, -3, -3, -1, 3,
-7, -6, 1, -5, -5, -3, 1 ) ) ;
## Cost matrix
costmx <- diffmx^2;
## Compute the alignment
al <- dtw(costmx,step.pattern=mvmStepPattern(10), keep.internals = TRUE)
## Elements 4,5 are skipped
print(al$index2)
plot(al,main="Minimum Variance Matching alignment")
```

### 10.stepPattern 
DTW的步进模式，Steppattern对象列出搜索最小距离路径时允许的转换，是累计成本矩阵的算法
```
## Well-known step patterns
symmetric1:
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: NA

symmetric2：
g[i,j] = min(
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
asymmetric：
g[i,j] = min(
     g[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
## Step patterns classified according to Rabiner-Juang [Rabiner1993]
rabinerJuangStepPattern(type,slope.weighting="d",smoothed=FALSE)

## Slope-constrained step patterns from Sakoe-Chiba [Sakoe1978]
symmetricP0：
g[i,j] = min(
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
asymmetricP0：
g[i,j] = min(
     g[i  ,j-1] + 0 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
symmetricP05：
g[i,j] = min(
     g[i-1,j-3] + 2 * d[i  ,j-2] +     d[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] + 2 * d[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-2,j-1] + 2 * d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-3,j-1] + 2 * d[i-2,j  ] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
asymmetricP05：
g[i,j] = min(
     g[i-1,j-3] +0.33 * d[i  ,j-2] +0.33 * d[i  ,j-1] +0.33 * d[i  ,j  ] ,
     g[i-1,j-2] +0.5 * d[i  ,j-1] +0.5 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-3,j-1] +     d[i-2,j  ] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
symmetricP1：
g[i,j] = min(
     g[i-1,j-2] + 2 * d[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-2,j-1] + 2 * d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
asymmetricP1：
g[i,j] = min(
     g[i-1,j-2] +0.5 * d[i  ,j-1] +0.5 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
symmetricP2：
g[i,j] = min(
     g[i-2,j-3] + 2 * d[i-1,j-2] + 2 * d[i  ,j-1] +     d[i  ,j  ] ,
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-3,j-2] + 2 * d[i-2,j-1] + 2 * d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M

asymmetricP2：
g[i,j] = min(
     g[i-2,j-3] +0.67 * d[i-1,j-2] +0.67 * d[i  ,j-1] +0.67 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-3,j-2] +     d[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
## Step patterns classified according to Rabiner-Myers [Myers1980]
typeIa：
g[i,j] = min(
     g[i-2,j-1] +     d[i-1,j  ] + 0 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j-1] + 0 * d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIb：
g[i,j] = min(
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j-1] +     d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIc：
g[i,j] = min(
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j-1] + 0 * d[i  ,j  ] ,
  )

 Normalization hint: N
 
typeId：
g[i,j] = min(
     g[i-2,j-1] + 2 * d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-1,j-2] + 2 * d[i  ,j-1] +     d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
typeIas：
g[i,j] = min(
     g[i-2,j-1] +0.5 * d[i-1,j  ] +0.5 * d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +0.5 * d[i  ,j-1] +0.5 * d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIbs：
g[i,j] = min(
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j-1] +     d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIcs：
g[i,j] = min(
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +0.5 * d[i  ,j-1] +0.5 * d[i  ,j  ] ,
  )

 Normalization hint: N
 
typeIds # smoothed
g[i,j] = min(
     g[i-2,j-1] +1.5 * d[i-1,j  ] +1.5 * d[i  ,j  ] ,
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-1,j-2] +1.5 * d[i  ,j-1] +1.5 * d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
typeIIa:
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j  ] ,
     g[i-2,j-1] +     d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIIb:
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] + 2 * d[i  ,j  ] ,
     g[i-2,j-1] + 2 * d[i  ,j  ] ,
  )

 Normalization hint: NA
 
typeIIc:
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j  ] ,
     g[i-2,j-1] + 2 * d[i  ,j  ] ,
  )

 Normalization hint: N
 
typeIId:
g[i,j] = min(
     g[i-1,j-1] + 2 * d[i  ,j  ] ,
     g[i-1,j-2] + 3 * d[i  ,j  ] ,
     g[i-2,j-1] + 3 * d[i  ,j  ] ,
  )

 Normalization hint: N+M
 
typeIIIc:
g[i,j] = min(
     g[i-1,j-2] +     d[i  ,j  ] ,
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-2,j-2] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
typeIVc：
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
     g[i-1,j-2] +     d[i  ,j  ] ,
     g[i-1,j-3] +     d[i  ,j  ] ,
     g[i-2,j-1] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-2,j-2] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-2,j-3] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-3,j-1] +     d[i-2,j  ] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-3,j-2] +     d[i-2,j  ] +     d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-3,j-3] +     d[i-2,j  ] +     d[i-1,j  ] +     d[i  ,j  ] ,
  )

 Normalization hint: N
 
## Miscellaneous
mori2006：
g[i,j] = min(
     g[i-2,j-1] + 2 * d[i-1,j  ] +     d[i  ,j  ] ,
     g[i-1,j-1] + 3 * d[i  ,j  ] ,
     g[i-1,j-2] + 3 * d[i  ,j-1] + 3 * d[i  ,j  ] ,
  )

 Normalization hint: M
 
rigid：
g[i,j] = min(
     g[i-1,j-1] +     d[i  ,j  ] ,
  )

 Normalization hint: N
```

#### 代码示例
```{r}
#########
##
## The usual (normalizable) symmetric step pattern
## Step pattern recursion, defined as:
## g[i,j] = min(
## g[i,j-1] + d[i,j] ,
## g[i-1,j-1] + 2 * d[i,j] ,
## g[i-1,j] + d[i,j] ,
## )
print(symmetric2) # or just "symmetric2"
#########
##
## The well-known plotting style for step patterns
plot(symmetricP2,main="Sakoe's Symmetric P=2 recursion")

#########
##
## Same example seen in ?dtw , now with asymmetric step pattern
idx<-seq(0,6.28,len=100);
query<-sin(idx)+runif(100)/10;
reference<-cos(idx);


## Do the computation
asy<-dtw(query,reference,keep=TRUE,step=asymmetric);
dtwPlot(asy,type="density",main="Sine and cosine, asymmetric step")
#########
##
## Hand-checkable example given in [Myers1980] p 61
##
`tm` <-
structure(c(1, 3, 4, 4, 5, 2, 2, 3, 3, 4, 3, 1, 1, 1, 3, 4, 2,
3, 3, 2, 5, 3, 4, 4, 1), .Dim = c(5L, 5L))
```


### 11.triangleFixing
度量距离的三角定位算法

#### 代码示例
```{r}
a<-matrix(0.2, 4,4)
a[4,2]<-0.8
a<-as.matrix(as.dist(a))
af<-triangleFixing(a)
tri.ineq.show(a)
stopifnot(is.null(tri.ineq.show(af)))
## Example in http://suvrit.de/work/soft/metricn.html
a<-matrix(c(0, 3, 7,
3, 0, 1,
7, 1, 0),3)
af<-triangleFixing(a)
tri.ineq.show(a)
stopifnot(is.null(tri.ineq.show(af)))
```

### 12.warp
对给定的时间序列应用扭曲

#### 代码示例
```{r}
idx<-seq(0,6.28,len=100);
query<-sin(idx)+runif(100)/10;
reference<-cos(idx)
alignment<-dtw(query,reference);
wq<-warp(alignment,index.reference=FALSE);
wt<-warp(alignment,index.reference=TRUE);
old.par <- par(no.readonly = TRUE);
par(mfrow=c(2,1));
plot(reference,main="Warping query");
lines(query[wq],col="blue");
plot(query,type="l",col="blue",
main="Warping reference");
points(reference[wt])
```

### 13.warpArea 
计算翘曲路径面积

#### 代码示例
```{r}
ds<-dtw(1:4,1:8);
plot(ds);
lines(seq(1,8,len=4),col="red");
warpArea(ds)
```

```
## Result: 6
## index 2 is 2 while diag is 3.3 (+1.3)
## 3 3 5.7 (+2.7)
## 4 4:8 (avg to 6) 8 (+2 )
## --------
## 6
```


