---
title: "TSdist2"
author: "haoyi.li"
date: "2018年11月15日"
output:
  html_document:
    df_print: kable
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
Sys.getlocale()
Sys.setlocale(locale="C") # 解决input string 1 is invalid in this locale的问题
knitr::opts_chunk$set(echo = TRUE)
library(TSdist)
```

# LBKeoghDistance
LB_Keogh for DTW

## 描述
Computes the Keogh lower bound for the Dynamic Time Warping distance between a pair of numeric time series.
计算一对数值时间序列之间的动态时间规整距离的Keogh下界。

## 用法
```
LBKeoghDistance(x, y, window.size)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
window.size：窗口大小
```

## 示例
```{r}
# The objects example.series1 and example.series2 are two
# numeric series of length 100 contained in the TSdist package.
data(example.series1)
data(example.series2)

# Calculate the LB_Keogh distance measure for these two series
# with a window of band of width 11:
LBKeoghDistance(example.series1, example.series2, window.size=11)
```

# LCSSDistance 
Longest Common Subsequence distance for Real Sequences.
实序列的最长公共子序列距离

## 描述
Computes the Longest Common Subsequence distance between a pair of numeric time series.
计算两个数值时间序列之间最长的公共子序列距离。

## 用法
```
LCSSDistance(x, y, epsilon, sigma)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
epsilon：一个定义距离的正阈值
sigma：必要时，可以通过指定一个正整数来添加sako-chiba窗口大小
```

## 示例
```{r}
# The objects example.series3 and example.series4 are two
# numeric series of length 100 and 120 contained in the TSdist
# package.
data(example.series3)
data(example.series4)

# Calculate the LCSS distance for two series of different length
# with no windowing constraint:
LCSSDistance(example.series3, example.series4, epsilon=0.1)

# Calculate the LCSS distance for two series of different length
# with a window of size 30:
LCSSDistance(example.series3, example.series4, epsilon=0.1, sigma=30)
```


# LPDistance 
Lp distances.

## 描述
Computes the distance based on the chosen Lp norm between a pair of numeric vectors.
根据选定的Lp范数计算一对数值向量之间的距离

## 用法
```
LPDistance(x, y, method="euclidean", ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
method：取值 "euclidean", "manhattan", "infnorm", "minkowski".
...：如果method="minkowski"，必须为p指定一个正整数.
```

## 示例
```{r}
# Compute the different Lp distances 
#Euclidean distance欧几里得距离
LPDistance(example.series1, example.series2, method="euclidean")

# Manhattan distance 曼哈顿距离
LPDistance(example.series1, example.series2, method="manhattan")

# Infinite norm distance无限范数距离
LPDistance(example.series1, example.series2, method="infnorm")

# Minkowski distance with p=3. 闵可夫距离
LPDistance(example.series1, example.series2, method="minkowski", p=3)
```


# ManhattanDistance 
Manhattan distance.曼哈顿距离

## 描述
Computes the Manhattan distance between a pair of numeric vectors.
计算两个数值向量之间的曼哈顿距离

## 用法
```
ManhattanDistance(x, y)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
```

## 示例
```{r}
# Compute the Manhattan distance between them:
ManhattanDistance(example.series1, example.series2)
```


# MindistSaxDistance
Symbolic Aggregate Aproximation based dissimilarity
基于符号聚合近似的差异性

## 描述
Calculates the dissimilarity between two numerical series based on the distance between their SAX representations.
基于符号聚合近似距离，计算两个数值时间序列的差异性

## 用法
```
MindistSaxDistance(x, y, w, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
w：The amount of equal sized windows that the series will be reduced to.
...：其他附加参数
```

## 示例
```{r}
# Calculate the mindist.sax distance between the two series using
# 20 equal sized windows for each series. The rest of the parameters
# are left in their default mode.
MindistSaxDistance(example.series3, example.series4, w=20)
```


# MinkowskiDistance 
Minkowski distance.

## 描述
Computes the Minkowski distance between two numeric vectors for a given p.

## 用法
```
MinkowskiDistance(x, y, p)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
p：A strictly positive integer value that defines the chosen L p norm.
```

## 示例
```{r}
# Compute the Minkowski distance between them:
MinkowskiDistance(example.series1, example.series2, p=3)
```


# NCDDistance 
Normalized Compression based distance
基于归一化压缩的距离

## 描述
Calculates a normalized distance between two numerical series based on their compressed sizes.
根据压缩大小计算两个数值序列之间的归一化距离。

## 用法
```
NCDDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the normalized compression based distance between the two series
# using default parameter.
NCDDistance(example.series3, example.series4)
```


# OneNN 
1NN classification for a pair of train/test time series datasets.
1NN分类器，用于一对训练/测试时间序列数据集

## 描述
Given a specific distance measure, this function provides the 1NN classification values and the associated error for a specific train/test pair of time series databases.

## 用法
```
OneNN(train, trainc, test, testc, distance, ...)
```

## 参数说明
```
train：作为训练集的时间序列数据集，如一个数值matrix, list, mts对象, zoo对象，xts对象。
trainc：表示训练集中每一个系列类别的数值向量。
test：作为测试集的时间序列数据集，如一个数值matrix, list, mts对象,
testc：表示测试集中每一个系列类别的数值向量。
distance：使用地距离度量， 取值其中之一: "euclidean", "manhattan",
"minkowski", "infnorm", "ccor", "sts", "dtw", "keogh_lb", "edr", "erp", "lcss", "fourier", "tquest", "dissimfull", "dissimapprox", "acf", "pacf", "ar.lpc.ceps", "ar.mah", "ar.mah.statistic", "ar.mah.pvalue", "ar.pic", "cdm", "cid", "cor", "cort", "wav", "int.per", "per", "mindist.sax", "ncd", "pred", "spec.glk", "spec.isd", "spec.llr", "pdc", "frechet")
...：所选择的距离函数的其他附加参数
```

## 示例
```{r}
# 加载数据集
data(example.database2)
str(example.database2)
# example.database2$data 是一个数值矩阵，每一行表示一个序列
# example.database2$classes 是一个数值向量，每个序列的分类
# Create train/test by dividing the dataset 70%-30%
# 将数据集分为训练集和测试集，序列数分别占70%和30%
set.seed(100) # 设置随机种子
trainindex <- sample(1:100, 70, replace=FALSE) # 使用随机函数产生训练集的索引
train <- example.database2[[1]][trainindex, ] # 提取训练集
test <- example.database2[[1]][-trainindex, ] # 提取测试集
trainclass <- example.database2[[2]][trainindex] # 训练集分类类别
testclass <- example.database2[[2]][-trainindex] # 测试集分类类别

# 基于不同的距离度量使用1NN分类器进行分类
OneNN(train, trainclass, test, testclass, "euclidean")
OneNN(train, trainclass, test, testclass, "pdc")
obj <- OneNN(train = train, trainc = trainclass, test = test, testc = testclass, distance =  "dtw")
OneNN(train = train, trainc = trainclass, test = test, testc = testclass, distance =  "fourier")
```


# PACFDistance
Partial Autocorrelation-based Dissimilarity
基于偏自相关的差异性

## 描述
Computes the dissimilarity between a pair of numeric time series based on their estimated partial autocorrelation coefficients.
基于估计的偏自相关系数，计算一对数值时间序列的差异性

## 用法
```
PACFDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the autocorrelation based distance between the two series using
# the default parameters:
PACFDistance(example.series3, example.series4)
```


# PDCDistance
Permutation Distribution Distance
置换分布距离

## 描述
Calculates the permutation distribution distance between two numerical series of the same length.
计算两个等长的数值序列之间的置换分布距离

## 用法
```
PDCDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the normalized compression based distance between the two series
# using the default parameters.
PDCDistance(example.series1, example.series2)
```


# PerDistance 
Periodogram based dissimilarity
基于周期图的差异性

## 描述
基于周期图，计算一对等长数值时间序列的差异性

## 用法
```
PerDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the ar.mah distance between the two series using
# the default parameters.
PerDistance(example.series1, example.series2)
```


# PredDistance 

Dissimilarity Measure Based on Nonparametric Forecasts  
基于非参数预测的差异测度

## 描述
The dissimilarity of two numerical series of the same length is calculated based on the L1 distance between the kernel estimators of their forecast densities at a given time horizon.  
在给定时间范围，根据预测密度的核估计量的L1距离，计算两个相同长度的数值序列的差异

## 用法
```
PredDistance(x, y, h, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
h：Integer value representing the prediction horizon.
...：其他附加参数
```

## 示例
```{r}
# Calculate the prediction based distance between the two series using
# the default parameters.
PredDistance(example.series1, example.series2)
```


# SpecGLKDistance 
Dissimilarity based on the Generalized Likelihood Ratio Test  
基于广义似然比检验的差异

## 描述
The dissimilarity of two numerical series of the same length is calculated based on an adaptation of the generalized likelihood ratio test.  
基于自适应的广义似然比检验，计算两个等长数值序列的差异性。

## 用法
```
SpecGLKDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the ar.mah distance between the two series using
# the default parameters.
SpecGLKDistance(example.series1, example.series2)
```


# SpecISDDistance  对数倒谱距离
Dissimilarity Based on the Integrated Squared Difference between the Log-Spectra
基于对数倒谱的积分平方差的差异性


## 描述
The dissimilarity of two numerical series of the same length is calculated based on the integrated squared difference between the non-parametric estimators of their log-spectra.  
基于对数倒谱的非参数估计的积分平方差，计算两个等长数值时间序列差异性

## 用法
```
SpecISDDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the spec.isd distance between the two series using
# the default parameters.
SpecISDDistance(example.series1, example.series2)
```


# SpecLLRDistance 
General Spectral Dissimilarity Measure Using Local-Linear Estimation of the Log-Spectra  
基于对数倒谱的局部线性估计的通用谱差异性度量

## 描述
The dissimilarity of two numerical series of the same length is calculated based on the ratio between local linear estimations of the log-spectras.
基于对数谱局部线性估计的比值，计算两个相同长度的数值序列的差异性

## 用法
```
SpecLLRDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：其他附加参数
```

## 示例
```{r}
# Calculate the spec.isd distance between the two series using
# the default parameters.
SpecLLRDistance(example.series1, example.series2)
```


# STSDistance 
Short time series distance (STS).  
短时序列距离

## 描述
Computes the Short Time Series Distance between a pair of numeric time series.  
计算一对数值序列的短时序距离

## 用法
```
STSDistance(x, y, tx, ty)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
tx：If not constant, a numeric vector that specifies the sampling index of series x.
ty：If not constant, a numeric vector that specifies the sampling index of series y.
```

## 示例
```{r}
# Calculate the STS distance assuming even sampling:
STSDistance(example.series1, example.series2)
# Calculate the STS distance providing an uneven sampling:
tx<-unique(c(seq(2, 175, 2), seq(7, 175, 7)))
tx <- tx[order(tx)]
ty <- tx
STSDistance(example.series1, example.series2, tx, ty)
```

# TquestDistance 
Tquest distance.  
任务距离

## 描述
Computes the Tquest distance between a pair of numeric vectors.  
计算一对数值向量之间的tquest距离

## 用法
```
TquestDistance(x, y, tx, ty, tau)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
tx：If not constant, a numeric vector that specifies the sampling index of series x. 如果不是常数，则表示指定系列x的抽样索引的数字向量。
ty：If not constant, a numeric vector that specifies the sampling index of series y. 如果不是常数，则表示指定系列y的抽样索引的数字向量。
tau：Parameter (threshold) used to define the threshold passing intervals. 指定间隔的阈值
```

## 示例
```{r}
# Calculate the Tquest distance assuming even sampling:
TquestDistance(example.series1, example.series2, tau=2.5)

# Calculate the Tquest distance for two series of different length:
TquestDistance(example.series3, example.series4, tau=2.5)
```

# TSDatabaseDistances 
TSdist distance matrix computation.  
Tdist距离矩阵计算

## 描述
TSdist distance matrix computation for time series databases.  
时间序列数据库的TS距离矩阵计算。

## 用法
```
TSDatabaseDistances(X, Y=NULL, distance, ...)
```

## 参数说明
```
X：时间序列数据库，可为一个数值矩阵，list，mts对象，zoo或者xts对象。
Y：时间序列数据库，可为一个数值矩阵，list，mts对象，zoo或者xts对象。 只为计算两个不同数据库之间的距离矩阵而定义，因此默认值为NULL。
distance：距离度量，取值其中之一: "euclidean", "manhattan", "minkowski", "infnorm", "ccor", "sts", "dtw", "keogh.lb", "edr", "erp", "lcss", "fourier", "tquest", "dissim", "acf", "pacf", "ar.lpc.ceps", "ar.mah", "ar.mah.statistic", "ar.mah.pvalue", "ar.pic", "cdm", "cid", "cor", "cort", "wav", "int.per", "per", "mindist.sax", "ncd", "pred", "spec.glk", "spec.isd", "spec.llr", "pdc", "frechet"
...：所选择的的距离函数的附加参数
```

## 示例
```{r}
data(example.database)
# To calculate the distance matrix of this database:
TSDatabaseDistances(example.database, distance="manhattan")
TSDatabaseDistances(example.database, distance="edr", epsilon=0.2)
TSDatabaseDistances(example.database, distance="fourier", n=20)
# The object zoo.database is a zoo object that saves
# the same 6 ARIMA time series saved in example.database.
data(zoo.database)
# To calculate the distance matrix of this database:
TSDatabaseDistances(zoo.database, distance="manhattan")
TSDatabaseDistances(zoo.database, distance="edr", epsilon=0.2)
TSDatabaseDistances(zoo.database, distance="fourier", n=20)
```

# TSDistances 
Tdist距离计算

## 描述
两个时间序列间的TIST距离计算。

## 用法
```
TSDistances(x, y, tx, ty, distance, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
tx：如果不是常数，则表示指定系列x的抽样索引的数字向量。
ty：如果不是常数，则表示指定系列y的抽样索引的数字向量。.
distance：距离函数. 取值其中之一: "euclidean", "manhattan", "minkowski", "infnorm", "ccor", "sts", "dtw", "keogh.lb", "edr", "erp", "lcss", "fourier", "tquest", "dissim", "acf", "pacf", "ar.lpc.ceps", "ar.mah", "ar.mah.statistic", "ar.mah.pvalue", "ar.pic", "cdm", "cid", "cor", "cort", "wav", "int.per", "per", "mindist.sax", "ncd", "pred", "spec.glk", "spec.isd", "spec.llr", "pdc", "frechet"
...：距离函数的附加参数
```

## 示例
```{r}
# The objects zoo.series1 and zoo.series2 are two
# zoo objects that save two series of length 100.
data(zoo.series1)
data(zoo.series2)
# For information on their generation and shape see
# help page of example.series.
# help(example.series)
# The distance calculation for these two series is done
# as follows:
TSDistances(zoo.series1, zoo.series2, distance="infnorm")
TSDistances(zoo.series1, zoo.series2, distance="cor", beta=3)
TSDistances(zoo.series1, zoo.series2, distance="dtw", sigma=20)
```

# WavDistance  
Dissimilarity for Time Series Based on Wavelet Feature Extraction  
基于小波特征提取的时间序列差异性

## 描述
Provides the dissimilarity between two numerical series of the same length by calculating the Euclidean distance between the wavelet coefficients obtained from an orthogonal wavelet transform of the series.  
通过计算由正交小波变换得到的小波系数之间的欧几里德距离，给出两个等长数值序列之间的差异性。

## 用法 
```
WavDistance(x, y, ...)
```

## 参数说明
```
x：第一个数值时间序列
y：第二个数值时间序列
...：附加参数
```

## 示例
```{r}
# Calculate the distance based on wavelet feature extraction between the series.
WavDistance(example.series1, example.series2)
```